
\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{geometry}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{bottom=0.5in, right=0.75in}

\addtolength{\oddsidemargin}{-1in}
\addtolength{\evensidemargin}{-1in}
\addtolength{\textwidth}{1.25in}
\addtolength{\topmargin}{-1.25in}
\addtolength{\textheight}{1.25in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ : #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Alex Johnson} \\[8pt]
    \small
    \faPhone ~ \href{tel:+1 (555) 867-5309}{+1 (555) 867-5309} ~|~ 
    \faEnvelope ~ \href{mailto:alex.johnson@email.com}{alex.johnson@email.com} ~|~ 
    \faLinkedin ~ \href{https://linkedin.com/in/alexjohnson}{linkedin.com/in/alexjohnson} ~|~ 
    \faGithub ~ \href{https://github.com/alexjohnson}{github.com/alexjohnson}
\end{center}

\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Illinois Urbana-Champaign}{Champaign, IL}
      {Bachelor of Science in Computer Science GPA:3.85 / 4.00}{August 2020 - May 2024}

      \textbf{Courses:}
        Data Structures, Operating Systems, Machine Learning, Distributed Systems.
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeSubHeadingListStart

    \resumeSubItem{Languages}{Python, Java, TypeScript, Go, SQL}
    \resumeSubItem{Frameworks \& Libraries}{FastAPI, React, Node.js, PyTorch, Spring Boot}
    \resumeSubItem{Tools \& Platforms}{Docker, Kubernetes, AWS, PostgreSQL, Redis, Git}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern}{San Francisco, CA}
      {Stripe}{May 2023 - August 2023}
      \resumeItemListStart
      
    \resumeItemWithoutTitle{Reduced API response latency by 35\% by introducing Redis caching for high-frequency payment queries.}
    \resumeItemWithoutTitle{Built an internal dashboard using React and TypeScript to monitor real-time transaction anomalies.}
    \resumeItemWithoutTitle{Collaborated with a team of 5 engineers to migrate 3 legacy microservices to a Kubernetes-based architecture.}
      \resumeItemListEnd
    \resumeSubheading
      {Undergraduate Research Assistant}{Champaign, IL}
      {UIUC Systems Lab}{January 2023 - May 2023}
      \resumeItemListStart
      
    \resumeItemWithoutTitle{Implemented a fault-tolerant distributed key-value store using the Raft consensus algorithm in Go.}
    \resumeItemWithoutTitle{Authored benchmarking scripts that reduced manual testing time by 60\% across 4 research projects.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {DevPortfolio AI}{}
      {Self-Initiated Project}{January 2024 - March 2024}
    \begin{itemize}
        \item Built a full-stack web app that uses GPT-4 to generate tailored resumes and cover letters from a user's GitHub activity.
    \item Designed a REST API with FastAPI and deployed on AWS EC2 with a CI/CD pipeline via GitHub Actions.
    \item Achieved 200+ active users within the first month of launch.
    \end{itemize}
    \resumeSubheading
      {Distributed File System}{}
      {Academic Project}{September 2023 - December 2023}
    \begin{itemize}
        \item Designed and implemented a distributed file system in Python supporting concurrent reads/writes across 10 nodes.
    \item Applied consistent hashing for load balancing, achieving uniform data distribution with less than 5\% variance.
    \end{itemize}
  \resumeSubHeadingListEnd

\end{document}
