
\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{geometry}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{bottom=0.5in, right=0.75in}

\addtolength{\oddsidemargin}{-1in}
\addtolength{\evensidemargin}{-1in}
\addtolength{\textwidth}{1.25in}
\addtolength{\topmargin}{-1.25in}
\addtolength{\textheight}{1.25in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ : #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Jordan M. Reyes} \\[8pt]
    \small
    \faPhone ~ \href{tel:+1 (415) 555-0198}{+1 (415) 555-0198} ~|~ 
    \faEnvelope ~ \href{mailto:jordan.reyes@pm.me}{jordan.reyes@pm.me} ~|~ 
    \faLinkedin ~ \href{https://linkedin.com/in/jordanmreyes}{linkedin.com/in/jordanmreyes} ~|~ 
    \faGithub ~ \href{https://github.com/jreyes}{github.com/jreyes}
\end{center}

\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {San José State University}{San José, CA}
      {Bachelor of Science in Software Engineering GPA:3.78 / 4.00}{August 2019 - May 2023}

      \textbf{Courses:}
        Data Structures \& Algorithms, Database Systems, Cloud Computing, Computer Networks.
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeSubHeadingListStart

    \resumeSubItem{Languages \& Runtimes}{TypeScript, Python, Go, SQL, Bash}
    \resumeSubItem{Frontend \& Frameworks}{React, Next.js, Tailwind CSS, Redux, Jest}
    \resumeSubItem{Backend \& APIs}{Node.js, Express, GraphQL, REST, gRPC}
    \resumeSubItem{Cloud \& DevOps}{AWS (Lambda, S3, RDS), Docker, GitHub Actions, Terraform, Prometheus}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern}{San Francisco, CA}
      {Stripe}{May 2023 - August 2023}
      \resumeItemListStart
      
    \resumeItemWithoutTitle{Refactored legacy checkout SDK in TypeScript, shrinking bundle size by 42\% \& cutting page-load time by 1.2s for 3.2M daily users.}
    \resumeItemWithoutTitle{Instrumented OpenTelemetry traces across 12 microservices, slashing mean time-to-detect outages from 18min to 4min.}
    \resumeItemWithoutTitle{Paired with 4 engineers to migrate 5 cron jobs to AWS Lambda, saving \$8k monthly compute cost.}
      \resumeItemListEnd
    \resumeSubheading
      {Undergraduate Teaching Assistant}{San José, CA}
      {SJSU CS Department}{January 2022 - May 2023}
      \resumeItemListStart
      
    \resumeItemWithoutTitle{Automated grading pipeline in Python that evaluated 1.4k student submissions per assignment with 98\% accuracy, freeing 10hrs/week for faculty.}
    \resumeItemWithoutTitle{Mentored 70+ students weekly, raising average project scores from 74\% to 86\% within one semester.}
    \resumeItemWithoutTitle{Deployed office-hours queue web app using React \& Firebase, reducing student wait time by 35\%.}
      \resumeItemListEnd
    \resumeSubheading
      {Freelance Full-Stack Developer}{Remote}
      {Self-Employed}{June 2021 - December 2022}
      \resumeItemListStart
      
    \resumeItemWithoutTitle{Architected multi-tenant e-commerce dashboard for 3 boutique retailers, processing \$50k monthly GMV via Stripe webhooks.}
    \resumeItemWithoutTitle{Integrated Algolia search, cutting average query latency to 120ms \& boosting conversion rate by 18\%.}
    \resumeItemWithoutTitle{Configured CI/CD with GitHub Actions, achieving 95\% test coverage \& zero-downtime deployments.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Global Carbon Offset Marketplace}{}
      {Self-Initiated Project}{January 2023 - April 2023}
    \begin{itemize}
        \item Bootstrapped Next.js marketplace where users purchase tokenized carbon credits, onboarding 1.1k users in 6 weeks.
    \item Wrote Solidity smart contracts on Polygon, reducing gas fees by 140x versus Ethereum mainnet.
    \item Implemented Chainlink oracle to verify 500k tCO2e offsets, ensuring 100\% on-chain transparency.
    \end{itemize}
    \resumeSubheading
      {Real-Time Wildfire Detection Mesh}{}
      {Academic Project}{September 2022 - December 2022}
    \begin{itemize}
        \item Assembled 25-node ESP32 sensor mesh streaming temperature \& VOC data every 5s to AWS IoT Core.
    \item Trained PyTorch CNN on 12k satellite images, attaining 92\% F1-score for fire ignition detection.
    \item Built React dashboard that pushed SMS alerts to 200+ Sonoma County residents within 60s of detection.
    \end{itemize}
    \resumeSubheading
      {Decentralized Health Record Wallet}{}
      {Professional Project}{May 2022 - August 2022}
    \begin{itemize}
        \item Delivered React Native mobile wallet encrypting 5k patient records via AES-256 \& storing IPFS hashes on Ethereum.
    \item Enabled QR-based consent flows, cutting clinic check-in time by 30s per patient across 3 pilot sites.
    \item Attained SOC-2 Type I readiness by automating 120 security controls using Terraform \& AWS Config.
    \end{itemize}
  \resumeSubHeadingListEnd

\end{document}
